---
title: "statistical_learning"
author: "xj2249"
date: "2019/11/26"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(glmnet)
```

# lasso
to use lasso, we'll look at "glmnet"
```{r}
bwt_df = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>%
  mutate(
    babysex = as.factor(babysex),
    babysex = fct_recode(babysex, "male" = "1", "female" = "2"),
    frace = as.factor(frace),
    frace = fct_recode(frace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4", "other" = "8"),
    malform = as.logical(malform),
    mrace = as.factor(mrace),
    mrace = fct_recode(mrace, "white" = "1", "black" = "2", "asian" = "3", 
                       "puerto rican" = "4")) %>% 
  sample_n(200)
```

get inputs for `glmnet`
```{r}
y = bwt_df$bwt
x = model.matrix(bwt~.,bwt_df)[,-1]
```

you don't have to do it, but it's useful to do.
```{r}
lambda = 10^(seq(3, -2, -0.1))

lasso_fit = 
        glmnet(x, y, lambda = lambda)

lasso_cv =
  cv.glmnet(x, y, lambda = lambda)

lambda_opt = lasso_cv$lambda.min
```

when lambda is very large, penalty term is everything and so only intercept in the model, when lambda is small, SSE matters, get more predators.
```{r}
broom::tidy(lasso_fit) %>% 
  select(term, lambda, estimate) %>% 
  complete(term, lambda, fill = list(estimate = 0) ) %>% 
  filter(term != "(Intercept)") %>% 
  ggplot(aes(x = log(lambda, 10), y = estimate, group = term, color = term)) + 
  geom_path() + 
  geom_vline(xintercept = log(lambda_opt, 10), color = "blue", size = 1.2) 
```
each line is a paremeter. 


```{r}
broom::tidy(lasso_cv) %>% 
  ggplot(aes(x = log(lambda, 10), y = estimate)) + 
  geom_point()  
```
estimate = prediction error
so the 1 is the best, with lowest prediction error

lasso is all about prediction.
you don't care about interpretaion, coefficient, significant.

**Make prediction with accuracy!**


# clustering
pick two continuous variables to do the clustering
```{r}
poke_df = 
  read_csv("./data/pokemon.csv") %>% 
  janitor::clean_names() %>% 
  select(hp, speed)
```

clustering work best with numerical variables(it's ok with categorical variable)

```{r}
poke_df %>% 
  ggplot(aes(x = hp, y = speed)) + 
  geom_point()
```

```{r}
kmeans_fit =
  kmeans(x = poke_df, centers = 3)


```

process and plot
```{r}
poke_df =
  broom::augment(kmeans_fit, poke_df)

poke_df %>% 
  ggplot(aes(x = hp, y = speed, color = .cluster)) +
  geom_point()
```

Points may change between clusters. but basically, it gives your some sense of the pattern,


## to see diff # of clusters. 
```{r}
clusts =
  tibble(k = 2:4) %>%
  mutate(
    km_fit =    map(k, ~kmeans(poke_df, .x)),
    augmented = map(km_fit, ~broom::augment(.x, poke_df))
  )

clusts %>% 
  select(-km_fit) %>% 
  unnest(augmented) %>% 
  ggplot(aes(hp, speed, color = .cluster)) +
  geom_point(aes(color = .cluster)) +
  facet_grid(~k)
```
may be three clusters is good.


# clustering: trajectories
very popular
```{r}
traj_data = 
  read_csv("./data/trajectories.csv")


traj_data %>% 
  ggplot(aes(x = week, y = value, group = subj)) + 
  geom_point() + 
  geom_path()
```


not tell your the control and experiment group
and let machine tell your that!(through clustering!!!)


## fit regression model for each subject to get the slope and intercept, and use this coefficient to do clustering. 
```{r}
int_slope_df = 
  traj_data %>% 
  nest(data = week:value) %>% 
  mutate(
    models = map(data, ~lm(value ~ week, data = .x)),
    result = map(models, broom::tidy)
  ) %>% 
  select(subj, result) %>% 
  unnest(result) %>% 
  select(subj, term, estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  rename(int = "(Intercept)", slope = week)

# select(int = "(Intercept)", slope = week)
# that's cool : do select and rename at the same time.
```

`pivot_wider` is cleaning the data, so we can do clusering as we did in the pokemon


```{r}
int_slope_df %>% 
  ggplot(aes(x = int, y = slope)) + 
  geom_point()
```


```{r}
km_fit = 
  kmeans(
    x = int_slope_df %>% select(-subj) %>% scale, 
    centers = 2)
# scale make things standardized

int_slope_df =
  broom::augment(km_fit, int_slope_df)
```

```{r}
int_slope_df %>% 
  ggplot(aes(x = int, y = slope, color = .cluster)) +
  geom_point()
```


```{r}
left_join(traj_data, int_slope_df) %>% 
  ggplot(aes(x = week, y = value, group = subj, color = .cluster)) + 
  geom_point() + 
  geom_path() 
```

kind of amazing. 
